A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-07-16 paper/paper.tex
paper: remove extraneous content

\subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a given set $S$ or as a set $T$ together with a map specifying for each element of the set $T$ on which index in $S$ it depends. In the first case, we call it an \emph{indexed} presentation. In the latter case, the set associated to a given index is the fiber, i.e. inverse image, of the index under the map, so we call it a \emph{fibered} presentation. The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others. In our experience, the opposition fibered/indexed is spontaneously understood by many listeners. In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories. The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type. (S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}
\begin{equation*}
  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) ~\simeq~ (T \rightarrow \U)\qquad \mbox{(indexed)}
\end{equation*}
where $\U$ represents sets in homotopy type theory as the subset of types with a unique proof of equality (within some universe).

>>>>

\subsection*{Fibered vs indexed presentation of semi-simplicial and semi-cubical sets}
A family of sets can commonly be represented in two ways: as a family properly speaking, indexed over a set $S$, or as a set $T$ together with a map specifying for each element of the set $T$ on which index it depends in $S$. In the first case, we call it an \emph{indexed} presentation. In the latter case, the set associated to a given index is the fiber, i.e. inverse image, of the index under the map, so we call it a \emph{fibered} presentation. The two presentations are equivalent and the equivalence can be phrased concisely in the language of homotopy type theory~\cite{hottbook} as a fibered/indexed correspondence\footnote{At a discussion on the Zulip channel for the HoTT community, alternative names fibration/family correspondence and unbundled/bundled correspondence were proposed, among others. In our experience, the opposition fibered/indexed is spontaneously understood by many listeners. In particular, it echoes to the Grothendieck construction of fibered categories from indexed categories. The most elementary instance of the correspondence, with $\Type$ instead of $\U$, that is $(\Sigma S: \Type. (S \rightarrow T)) \simeq (T \rightarrow \Type)$, is sometimes called ``Grothendieck construction for dummies'' (its proof requires univalence, see~\cite{hottbook}).}
\begin{equation*}
  \mbox{(fibered)}\qquad(\Sigma S: \U. (S \rightarrow T)) ~\simeq~ (T \rightarrow \U)\qquad \mbox{(indexed)}
\end{equation*}
where $\U$ represents sets in homotopy type theory as the subset of types with a unique proof of equality (within some universe).
